Topological Equivariant Artist Model

### 2022-01-27 slides/main.tex
valid artist
nu slides

               \onslide*<5-6|handout:1-2>{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
               \onslide*<7|handout:3>{\arrow[u, "\gsectionc \in \cgamma{\gbasec}{\gtotalc}"', bend right, pos=.5]}

@@

@@

\begin{frame}{"Valid" viz?}
    \begin{equation*}
        \label{eq:artist:artist_sheaf}
        \begin{tikzcd}[ampersand replacement = \&, column sep=tiny, row sep=huge]
            \onslide*<1-|handout:1>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \&  \& 
            \onslide*<2-|handout:1>{\textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
              \bigm{\vert} \vartistc \circ \dfuncc_{\dsectionc} \circ \dsectionc = \dfuncc_{\gsectionc} \circ \gsectionc \textcolor{set}{\big\}}} 
            \onslide*<2-|handout:1>{\arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white]} \\ 
            \&  \& \\
            \onslide*<1-|handout:1>{\opensetgc} 
            \onslide*<1-|handout:1>{\arrow[uu, "\sheafc_{\gtotalc}", color=sheaf, maps to]} 
            \onslide*<2-|handout:1>{\arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf, maps to]} 
            \&  \& 
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

\begin{frame}{Encoding + Assembly Stages}
    %E-V and Q diagram    
\end{frame}
\begin{frame}{Encoding + Assembly}
    \begin{figure}
        \includegraphics{../paper/figures/q_hat.p}
    \end{figure}
\end{frame}
\begin{frame}{Domain and Range}
    \begin{figure}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[.5\textwidth]{../paper/figures/fiberbundle.png}
        \end{subfigure}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[.5\textwidth]{../paper/figures/render.png}
        \end{subfigure}
    \end{figure}
\end{frame}

\begin{frame}{Example $\dfunctc$: Stevens' Scales \cite{stevensTheoryScalesMeasurement1946}}
\begin{table}[H]
    \begin{tabularx}{\textwidth}{|l|l|X|}\toprule
        \textbf{scale} & \textbf{group} & \textbf{constraint} \\\midrule
        nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
        ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
        interval &  translation &  $\vchannel (x + c) = \vchannel(x) + c$ \\
        ratio &  scaling &  $\vchannel(xc) = \vchannel(x)*c $\\ \bottomrule
    \end{tabularx}
\end{table}
\end{frame}

>>>>

               \onslide*<5-6|handout:1-2>{\arrow[u, "\dsectionc \in \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}"', bend right, pos=.5]}
               \onslide*<7|handout:3>{\arrow[u, "\gsectionc \in \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}"', bend right, pos=.5]}

@@

\begin{comment}
    \note{move this to top where I introduce data/graphics}
\begin{frame}{Domain and Range}
    \begin{figure}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[.5\textwidth]{../paper/figures/fiberbundle.png}
        \end{subfigure}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[.5\textwidth]{../paper/figures/render.png}
        \end{subfigure}
    \end{figure}
\end{frame}
\end{comment}

@@

\begin{frame}{"Valid" viz?}
    \begin{equation*}
        \label{eq:artist:artist_sheaf}
        \begin{tikzcd}[ampersand replacement = \&, column sep=tiny, row sep=huge]
            \onslide*<1-|handout:1>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \&  \& 
            \onslide*<2-|handout:1>{\textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
              \bigm{\vert} \delta(\vartistc(\dsectionc)) = \equivc(\dsectionc) \textcolor{set}{\big\}}} 
            \onslide*<2-|handout:1>{\arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white]} \\ 
            \&  \& \\
            \onslide*<1-|handout:1>{\opensetgc} 
            \onslide*<1-|handout:1>{\arrow[uu, "\sheafc_{\gtotalc}", color=sheaf, maps to]} 
            \onslide*<2-|handout:1>{\arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf, maps to]} 
            \&  \& 
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

\begin{frame}{Measurable Visual Components}
    \begin{columns}
        \column{0.31\textwidth}
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
                \onslide*<1|handout:1>{\vfiberc}
                \onslide*<1|handout:1>{\arrow[r, hook]} \& 
                \onslide*<1|handout:1>{\vtotalc} 
                \onslide*<1|handout:1>{\arrow[d, "\pi"']} \\
                \& 
                \onslide*<1|handout:1>{\dbasec} 
                \onslide*<1|handout:1>{\arrow[u, "\vsectionc \in \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}"', bend right, pos=.5]}
            \end{tikzcd}
        \end{equation*}
        \column{0.69\textwidth}
    \only<1|handout:1>{
        \begin{description}[style=nextline]
            \item[\textcolor{total}{Data \vtotalc}]{continuity + visual fields}
            \item[\textcolor{base}{Continuity \dbasec}]{data continuity}
            \item[\textcolor{fiber}{components \vfiberc}] {visual components \cite{bertinIIPropertiesGraphic2011} of a graphic, e.g. x and y position, area, color, line thickness}
        \end{description}
        }
    \end{columns}
    \pause 
    \only<1|handout:1>{
        \begin{alertblock}{}
            \begin{description}[style=nextline]
                \item[\textcolor{section}{visual Components}]{$\cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \coloneqq \big\{\vsectionc: \opensetc\rightarrow \vtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\vsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}$}
            \end{description}
        \end{alertblock}
    }
\end{frame}

\begin{frame}{Equivariant Data to Components: $\vchannel: \sheaf_{\dbasec,\dtotalc} \rightarrow \sheaf_{\dbasec, \vtotalc}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \arrow[rr, "\vchannelc"] \& \& 
            \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \\
             \& \opensetc 
             \arrow[lu, "{\sheafc_{\dbasec,\dtotalc}}" description, maps to] 
             \arrow[ru, "{\sheafc_{\dbasec, \vtotalc}}" description, maps to] \& 
            \end{tikzcd}
    \end{equation*}

    \begin{alertblock}{Build in Equivariance}
    implement $\vchannelc: \dsectionc \mapsto \vsectionc$ as a monoid homomorphism $\vchannelc: \dfuncc_{\dtotalc} \rightarrow \dfuncc_{\vtotalc}$ such that 
        \begin{description}
            \item[equivariance] $\vchannelc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ 
    \end{description} 
\end{alertblock}
\end{frame}

\begin{frame}{Sample $\dfuncc$: Stevens' Scales \cite{stevensTheoryScalesMeasurement1946}}
    \begin{table}[H]
        \begin{tabularx}{\textwidth}{|l|l|X|}\toprule
            \textbf{scale} & \textbf{group} & \textbf{constraint} \\\midrule
            nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
            ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
            interval &  translation &  $\vchannel (\delement + c) = \vchannel(\delement) + c$ \\
            ratio &  scaling &  $\vchannel(\delement* c) = \vchannel(\delement)*c $\\ \bottomrule
        \end{tabularx}
    \end{table}
\end{frame}

\begin{frame}{Shared Components: $\vchannelc = \prod\limits_{i=0}^{n}\vchannelc_i$}
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiberc_a\times \dfiberc_b 
            \arrow[rr, "\vchannelc"] 
            \arrow[rd, "p_{\dfiberc}"] \& \& \vfiberc_a\times \vfiberc_b 
            \arrow[rd, "p_{\vfiberc}"] \& \\    \& \dfiberc_{a} \arrow[rr, "\vchannelc_{a}", dashed] \& \& \vfiberc_a \\
            \dfiberc_a\times \dfiberc_c 
            \arrow[rr, "\vchannelc^{\prime}"] \arrow[ru, "p_{\dfiberc^{\prime}}"'] \& \& {\vfiberc_a}^{\prime}\times {\vfiberc_c}^{prime} \arrow[ru, "p_{\vfiberc^{\prime}}"'] \&           
            \end{tikzcd}
    \end{equation}
    \begin{alertblock}{Consistent Transformations \cite{hullmanKeeping2018}}
        if $p_{\dfiberc} = p_{\dfiberc^{\prime}}$ then $p_{\vfiberc}(\vchannelc(\dsectionc)) = p_{\vfiberc^{\prime}}(\vchannelc^{\prime}(\dsectionc^{\prime}))$ s.t. there exists a transformation $\vchannelc_a: \dfiberc_{a}\rightarrow \vfiberc_{a}$
    \end{alertblock}
\end{frame}

\begin{frame}{Components to Graphic}
    \begin{figure}
        \includegraphics{../paper/figures/q_hat.p}
    \end{figure}
\end{frame}
